\ttitle

### 2015-08-23 Tables/bc_at_new_indices.tex
Review 1 - Body Comp
- Major changes to text
- Spelling checked
- References checked
- No compile erros
- Couple of overfull boxes that cant be fixed

\begin{sidewaystable}[p]
	\caption{The relationship between body composition, body habitus and $\dot{V}_{O_2}$AT scaled using different factors in patients undergoing major pancreatic surgery.}
	\label{table:bc_at_new_indices}
	\footnotesize
	\centering
	\renewcommand{\arraystretch}{1.5} %Increases space between rows
	%\setlength{\tabcolsep}{9pt} %sets the space between columns
	%\hline\noalign{\smallskip} %increases space after the line
	\begin{tabular}{|l|cc|cc|cc|cc|cc|cc|}
		\hline
		& \multicolumn{2}{c|}{Absolute $\dot{V}_{O_2}$} & \multicolumn{2}{c|}{$\frac{\dot{V}_{O_2}}{Weight}$} & \multicolumn{2}{c|}{$\frac{\dot{V}_{O_2}}{Height^2}$} & \multicolumn{2}{c|}{$\frac{\dot{V}_{O_2}}{BMI}$} & \multicolumn{2}{c|}{$\frac{\dot{V}_{O_2}}{Skeletal\ Muscle}$}  & \multicolumn{2}{c|}{$\frac{\dot{V}_{O_2}}{Lean\ Body\ Mass}$}\\

>>>>

\begin{sidewaystable}[p]
	\caption{The relationship between body composition, body habitus and $\dot{V}_{O_2}$AT scaled using different factors (controlled for sex) in patients undergoing major pancreatic surgery.}
	\label{table:bc_at_new_indices}
	\footnotesize
	\centering
	\renewcommand{\arraystretch}{1.5} %Increases space between rows
	%\setlength{\tabcolsep}{9pt} %sets the space between columns
	%\hline\noalign{\smallskip} %increases space after the line
	\begin{tabular}{|l|cc|cc|cc|cc|cc|cc|}
		\hline
		& \multicolumn{2}{c|}{Absolute $\dot{V}_{O_2}$} & \multicolumn{2}{c|}{$\frac{\dot{V}_{O_2}}{Weight}$} & \multicolumn{2}{c|}{$\frac{\dot{V}_{O_2}}{Height^2}$} & \multicolumn{2}{c|}{$\frac{\dot{V}_{O_2}}{BMI}$} & \multicolumn{2}{c|}{$\frac{\dot{V}_{O_2}}{Skeletal\ Muscle}$}  & \multicolumn{2}{c|}{$\frac{\dot{V}_{O_2}}{Lean\ Body\ Mass}$}\\
